---
title: "Homework 04"
author: "Salomon Gilles - Credit to Andrew Abbott for inspiring me"
date: "May 31, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction:

We attempt to illustrate the Central Limit Theorem using R markdown and push it it to GitHub. We use a normal distribution with two different sample sizes and an exponential distribution with two different sample sizes.

### 1: Normal Distribution: samplesize = 150 and simulation = 1100
```{r}
n1 <- 150
nsimulations1 <- 1100
basepool1 <- rnorm(n1)
means.array1 <- numeric(nsimulations1)
for (index in 1:nsimulations1) {
        tempvar1 <- sample(basepool1, size = length(basepool1), replace = TRUE)
	means.array1[index] <- mean(tempvar1)
}
```

## Original pool1

The median and the mean are very far apart 
```{r}
summary(basepool1)
```


We can see that difference in distortions with the severity on either side 
```{r}
hist(basepool1)
```
## Means array

Notice the median and the mean are approximately equally distributed on the summary table 
```{r}
summary(means.array1)
hist(means.array1)
```

-----------------------------------------------------------------------------------------------------------------------------------

### 2: Normal Distribution: samplesize = 1100 and simulation = 1100
```{r}
n2 <- 1100
nsimulations2 <- 1100
basepool2 <- rnorm(n2)
means.array2 <- numeric(nsimulations2)
for (index in 1:nsimulations2) {
        tempvar2 <- sample(basepool2, size = length(basepool2), replace = TRUE)
	means.array2[index] <- mean(tempvar2)
}
```

## Original pool2

The median and the mean are even very far apart 
```{r}
summary(basepool2)
```


We can see that difference in distortions with the severity on either side 
```{r}
hist(basepool2)
```
## Means array2

Notice the median and the mean are still approximately closely distributed on the summary table 
```{r}
summary(means.array2)
hist(means.array2)
```

----------------------------------------------------------------------------------------------------------------------------------

### 3: Exponential Distribution: samplesize = 150 and simulation = 1100
```{r}
n3 <- 150
nsimulations3 <- 1100
basepool3 <- rexp(n3)
means.array3 <- numeric(nsimulations3)
for (index in 1:nsimulations3) {
        tempvar3 <- sample(basepool3, size = length(basepool3), replace = TRUE)
	means.array3[index] <- mean(tempvar3)
}
```

## Original pool3

The median and the mean are very far apart with only the right skewed
```{r}
summary(basepool3)
```


We can see that difference in distortions with the severity only on the right side 
```{r}
hist(basepool3)
```
## Means array3

Notice the median and the mean are approximately equally distributed on the summary table 
```{r}
summary(means.array3)
hist(means.array3)
```

----------------------------------------------------------------------------------------------------------------------------------

### 4: Exponential Distribution: samplesize = 1100 and simulation = 1100
```{r}
n4 <- 1100
nsimulations4 <- 1100
basepool4 <- rexp(n4)
means.array4 <- numeric(nsimulations4)
for (index in 1:nsimulations4) {
        tempvar4 <- sample(basepool4, size = length(basepool4), replace = TRUE)
	means.array4[index] <- mean(tempvar4)
}
```

## Original pool4

The median and the mean are even very far apart with only a right skewed observation 
```{r}
summary(basepool4)
```


We can see that difference in distortions with the severity on right side only
```{r}
hist(basepool4)
```
## Means array4

Notice the median and the mean are evenly distributed on the summary table 
```{r}
summary(means.array4)
hist(means.array4)
```

# Conclusion:

The illustration of the Central Limit Theorem demonstrates that the median and mean are approximately equal when your sample size is big and when you run large observation.This makes your result reliable. However, you cannot get results when your sample size is fairly small and when you.

